---
title: "ALL-closed"
author: "Siyan Wang"
date: "2023-12-03"
output: html_document
---
We first discuss the closed store and then the opening store. Finally we compare the service and ambiance difference on between these two kind of bakery store.

```{r setup, include=FALSE}
library(readr)
library(tidytext)
library(tidyverse)
library(dplyr)
library(wordcloud)
library(stringr)
library(reshape2)
```

# Read data
```{r ,message=FALSE}
all_review_data<-read_csv("bakery_reviews.csv")
########## close data ###################
close_data<-read_csv("all_closed_bakeries_reviews.csv")
close_bad_review<-read_csv("all_closed_bakeries_negative_reviews.csv")
close_good_review <- read_csv("all_closed_bakeries_positive_reviews.csv")
############ open data ###################
open_data<-read_csv("all_open_bakeries_reviews.csv")
open_bad_review<-read_csv("all_open_bakeries_negative_reviews.csv")
open_good_review <- read_csv("all_open_bakeries_positive_reviews.csv")
########## dictionary #############
food<- readLines("food.txt")
drink<-readLines("drink.txt")
ambiance<-readLines("ambiance.txt")
service<-readLines("service.txt")
par(mar = rep(0, 4)) # setting the margin
```

## Word
```{r}
tidy_all_data<-all_review_data%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all review wordcloud 
# with(count(tidy_close_data,word),
#      wordcloud(word,n,max.words = 100,
#                colors=brewer.pal(8, "Dark2"),random.order = FALSE))

show(tidy_all_data%>%
  count(word,sort = TRUE))
```
# closed store reviews analysis

```{r,warning=FALSE,message=FALSE}

#all closed reviews 

tidy_close_data<-close_data%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all review wordcloud 
with(count(tidy_close_data,word),
     wordcloud(word,n,max.words = 100,
               colors=brewer.pal(8, "Dark2"),random.order = FALSE))

show(tidy_close_data%>%
  count(word,sort = TRUE))
```



## CLOSE store positive review
```{r,warning=FALSE,message=FALSE}

#all reviews wordcloud

tidy_close_good_data<-close_good_review%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all goodreview wordcloud 
# with(count(tidy_good_data,word),
#      wordcloud(word,n,max.words = 100,
#                colors=brewer.pal(8, "Dark2")))

show(tidy_close_good_data%>%
  count(word,sort = TRUE))
```


```{r}
tidy_close_good_data%>%
  mutate(category = case_when(
    word %in% food ~ "food",
    word %in% drink ~ "drink",
    word %in% ambiance ~"ambiance",
    word %in% service ~ "service",
    TRUE ~ "other"
  ))%>%
  filter(category != "other") %>%  
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  comparison.cloud(max.words = 100,title.size=2,rot.per=0)
```
### service 
```{r}
pattern <- paste(service, collapse = "|")
pattern <- paste0("\\b(?:", pattern, ")\\b")

service_word_good_reviews<-
  # tidy_good_data%>%
  # select(-user_id,-review_id,date)%>% #delete three columns for convenience
  str_extract_all(tidy_good_data$word, pattern, simplify = TRUE)

service_word_good_reviews<-unlist(service_word_good_reviews)
  

wordcloud(words = service_word_good_reviews, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"),rot.per=0,random.order = FALSE)
```


## CLOSE negative review

```{r}
tidy_close_bad_data<-close_bad_review%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all goodreview wordcloud 
# with(count(tidy_good_data,word),
#      wordcloud(word,n,max.words = 100,
#                colors=brewer.pal(8, "Dark2")))

show(tidy_close_bad_data%>%
  count(word,sort = TRUE))
```

```{r}
tidy_close_bad_data%>%
  mutate(category = case_when(
    word %in% food ~ "food",
    word %in% drink ~ "drink",
    word %in% ambiance ~"ambiance",
    word %in% service ~ "service",
    TRUE ~ "other"
  ))%>%
  filter(category != "other") %>%  
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  comparison.cloud(max.words = 100,title.size=2,rot.per=0)
```

```{r}
service_close_bad_reviews<-
  # tidy_good_data%>%
  # select(-user_id,-review_id,date)%>% #delete three columns for convenience
  str_extract_all(tidy_close_bad_data$word, pattern, simplify = TRUE)

service_close_good_reviews<-unlist(service_close_bad_reviews)
  

wordcloud(words = service_close_bad_reviews, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"),rot.per=0)
```

## OPEN 
```{r}
#all open reviews 

tidy_open_data<-open_data%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all review wordcloud 
with(count(tidy_open_data,word),
     wordcloud(word,n,max.words = 100,
               colors=brewer.pal(8, "Dark2"),random.order = FALSE,rot.per=0))

show(tidy_open_data%>%
  count(word,sort = TRUE))
```
## OPEN store positive review

```{r,warning=FALSE,message=FALSE}

#all reviews wordcloud

tidy_open_good_data<-open_good_review%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all goodreview wordcloud 
# with(count(tidy_good_data,word),
#      wordcloud(word,n,max.words = 100,
#                colors=brewer.pal(8, "Dark2")))

show(tidy_open_good_data%>%
  count(word,sort = TRUE))
```
```{r}
tidy_open_good_data%>%
  mutate(category = case_when(
    word %in% food ~ "food",
    word %in% drink ~ "drink",
    word %in% ambiance ~"ambiance",
    word %in% service ~ "service",
    TRUE ~ "other"
  ))%>%
  filter(category != "other") %>%  
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  comparison.cloud(max.words = 100,title.size=2,rot.per=0)
```
### service 

```{r}
# pattern <- paste(service, collapse = "|")
# pattern <- paste0("\\b(?:", pattern, ")\\b")

service_open_good_reviews<-
  # tidy_good_data%>%
  # select(-user_id,-review_id,date)%>% #delete three columns for convenience
  str_extract_all(tidy_open_good_data$word, pattern, simplify = TRUE)

service_open_good_reviews<-unlist(service_open_good_reviews)
  

wordcloud(words = service_open_good_reviews, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"),rot.per=0,random.order = FALSE)
```
## OPEN negative review

```{r}
tidy_open_bad_data<-open_bad_review%>%
  #select(-user_id,-review_id)%>%
  unnest_tokens(word,text)%>% 
  anti_join(stop_words)%>%
  mutate(word = str_remove_all(word, "\\d+"))%>%
  filter(!word %in% c("",'.',",","..","'",'food','service','time','santa','barbara'))

#all goodreview wordcloud 
# with(count(tidy_good_data,word),
#      wordcloud(word,n,max.words = 100,
#                colors=brewer.pal(8, "Dark2")))

show(tidy_open_bad_data%>%
  count(word,sort = TRUE))
```

```{r}
tidy_open_bad_data%>%
  mutate(category = case_when(
    word %in% food ~ "food",
    word %in% drink ~ "drink",
    word %in% ambiance ~"ambiance",
    word %in% service ~ "service",
    TRUE ~ "other"
  ))%>%
  filter(category != "other") %>%  
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  comparison.cloud(max.words = 100,title.size=2,rot.per=0)
```

```{r}
service_open_bad_reviews<-
  # tidy_good_data%>%
  # select(-user_id,-review_id,date)%>% #delete three columns for convenience
  str_extract_all(tidy_open_bad_data$word, pattern, simplify = TRUE)

service_open_good_reviews<-unlist(service_word_bad_reviews)
  

wordcloud(words = service_open_bad_reviews, min.freq = 1, scale = c(3, 0.5), colors = brewer.pal(8, "Dark2"),rot.per=0,random.order = FALSE)
```

## Service analysis on open and close store

```{r}
all_data <- bind_rows(tidy_open_good_data %>% mutate(source = "open"),
                      tidy_close_bad_data %>% mutate(source = "close"))
#
# 筛选包含在 "service" 字典中的词汇
service_form <- all_data %>%
  filter(word %in% service)%>%
  mutate(category = case_when(
    source == "open" ~ "open",
    source == "close" ~ "close",
    TRUE ~ NA_character_
  ))%>%
  select(word, category)%>%
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  prop.table( margin = 2)

comparison.cloud(service_form,max.words = 100,title.size=2,rot.per=0)

#print(service_form)
#service_form<-rename(service_form, close =word)
 
```

## Food analysis on open and close store

```{r}
food_form <- all_data %>%
  filter(word %in% food)%>%
  mutate(category = case_when(
    source == "open" ~ "open",
    source == "close" ~ "close",
    TRUE ~ NA_character_
  ))%>%
  select(word, category)%>%
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  prop.table( margin = 2)

comparison.cloud(food_form,max.words = 100,title.size=2,rot.per=0)

```
## Drink analysis on open and close store

That maybe have no sense

```{r}
drink_form <- all_data %>%
  filter(word %in% drink)%>%
  mutate(category = case_when(
    source == "open" ~ "open",
    source == "close" ~ "close",
    TRUE ~ NA_character_
  ))%>%
  select(word, category)%>%
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  prop.table( margin = 2)

comparison.cloud(drink_form,max.words = 100,title.size=2,rot.per=0)
```
## Ambiance analysis on open and close store

```{r}
ambiance_form <- all_data %>%
  filter(word %in% ambiance)%>%
  mutate(category = case_when(
    source == "open" ~ "open",
    source == "close" ~ "close",
    TRUE ~ NA_character_
  ))%>%
  select(word, category)%>%
  count(word,category,sort = TRUE)%>%
  acast(word~category, value.var='n', fill=0)%>%
  prop.table( margin = 2)

comparison.cloud(ambiance_form,max.words = 100,title.size=2,rot.per=0)
```






